\section{Inheritance}
Inheritance allows to reduce code repetition by sharing behaviors and
data members between related types.

There are multiple types of inheritance

\subsection*{Interface}
It tells a class \textit{what} we want to implement not \textit{how}. It
allows to share and bound behaviors among unrelated classes. In a sense
it is a contract (a will) that the inheritors must satisfy.

Interfaces have only functions with declaration but no definition, and
they are called \textit{abstract classes} while inheritors are called
\textit{concrete classes}.

An interface creates a \textit{can support} relationship.

\subsection*{Subclassing Inheritance}
It is similar to the interface but the class may actually have some
code. Usually, that code is inherited by derived class. The ones without
code must be implemented, the ones with code can be overriden. Ideally
all subclasses must share the same interface and semantics as their
base.

Subclassing inheritance is creates a \textit{is-a} relationship.

It is susceptible to the fragile base class problem which describes a
problem where a change in the super class breaks the behavior of the
derived classes.

\textbf{Delegation} is an alternative to inheritance that create a
\textit{can use} relationship with another class. The popular saying
goes that ``prefer composition over inheritance''.

\subsection*{Implementation Inheritance}
Private inheritance in C++ summarizes this well. An inheritor gets the
implementations of the base class but not its public interface.

\subsection*{Inheritance Typing}
Inheritance creates new supertypes and subtypes of the related classes.
Types of interfaces are called reference types because they cannot be
instantiated directly.

\subsection*{Subtype Polymorphism}
Subtype Polymorphism is the ability to substitute an object of a subtype
(e.g., Circle) anywhere a supertype (e.g., Shape) is expected. More
technically, S.P. is where code designed to operate on an object of type
T operates on an object that is a subtype of T.

Dynamically typed languages cannot have subtype polymorphism. Duck
typing is note subtype polymorphism.
